Proposed Solution

### 2017-01-24 CAV17/secs/table2.tex
cav17: translator section

\begin{table*}[tbp]
\centering
\caption{Sampled misconfiguration files for error detection evaluation.}
\label{table-casestudy}
\begin{footnotesize}
\begin{tabular}{|c|c|c|c|c|}
\hline
{\bf Error Type} & {\bf Problem Description} & 
{\bf \app Report}  & {\bf Rank w/o} & {\bf Rank w/}\\ 
\hline
\hline
Order & Cannot allocate memory for the buffer pool~\cite{innod-ordering}  
& \ennan{example 4}
& ~ & ~ \\ \hline

Missing & MySQL missing key\_buffer in my.cnf~\cite{missing}
& \ennan{missing key\_buffer}
& ~ & ~ \\ \hline

Type & MySQL cannot start~\cite{querylog}
& \ennan{example 3}
& ~
& ~ \\ \hline

Fine-Grain & MySQL load is very high~\cite{correlation}   
& \ennan{results in example 2) }
& ~ 
& ~ \\ \hline

Coarse-Grain & MySQL server has gone away error~\cite{coarse-grain}
& \ennan{results}
& ~ 
& ~ \\ \hline

>>>>

\begin{table*}[tbp]
\centering
\caption{Sampled misconfiguration files for error detection evaluation.}
\label{table-casestudy}
\begin{footnotesize}
\begin{tabular}{|c|c|c|c|}
\hline
{\bf Errors} & {\bf URLs} & {\bf Rank w/o} & {\bf Rank w/}\\ 
\hline
\hline
\multirow{3}{*}{MISSING ERROR: Expected "key-buffer"} & url & 7 & 8 \\
\multirow{3} & url & 9 & 10 \\ 
& url & 11 & 12 \\ 
\hline

\multirow{3}{*}{Ordering} & url & 7 & 8 \\ & url & 9 & 10 \\
& url & 11 & 12 \\  
\hline

\multirow{3}{*}{Type error} & url & 7 & 8 \\ & url & 9 & 10 \\  
& url & 11 & 12 \\
\hline

\multirow{3}{*}{fine-grained} & url & 7 & 8 \\ & url & 9 & 10 \\  
& url & 11 & 12 \\
\hline

\multirow{3}{*}{int correlation} & url & 7 & 8 \\ & url & 9 & 10 \\  
& url & 11 & 12 \\
\hline

### 2017-01-24 CAV17/secs/trans.tex
cav17: translator section

\begin{figure}[!htb]
    \centering
    \begin{minipage}{.25\textwidth}
	\begin{lstlisting} [label={lst:1.cnf},language=C,caption={1.cnf}]
[server]
foo = ON
[client]
bar = 1
	\end{lstlisting}
    \end{minipage}%
    \hspace{1cm}
    \begin{minipage}{0.25\textwidth}
	\begin{lstlisting} [label={lst:2.cnf},language=C,caption={2.cnf}]
[server]
foo = ON
[client]
bar = ON
	\end{lstlisting}
    \end{minipage}
    \hspace{1cm}
    \begin{minipage}{0.25\textwidth}
	\begin{lstlisting} [label={lst:2.cnf},language=C,caption={3.cnf}]
[server]
foo = OFF
[client]
bar = OFF
	\end{lstlisting}
    \end{minipage}
    \caption{A learning set of configuration files}
    \label{fig:tset}
\end{figure}

\subsection{Probabilistic Types}
\label{sec:ptypes}
An additional challenge is that it is not always possible to fully determine the type of key based on a single example value. 
For this reason, we introduce \textit{probabilistic types}, as contrasted with \textit{basic types}.
In \app, the set of basic types contains strings, file paths, integers, sizes, and booleans. 
Taking the configuration \ref{lst:1.cnf}, we can assume {\tt foo} is a boolean type by the grammar of MySQL,
  but the keyword {\tt bar} could either be a integer type or a boolean type.
Consider that we would like to learn a rule that the boolean keywords should have the same values ($eq(\texttt{foo},\texttt{bar})$).
We then have two potential situations; in the first case where {\tt bar}$::int$, we do not learn the above rule, but in the second case where {\tt bar}$::bool$, the rule is valid.
To resolve this ambiguity, instead of immediately assigning one type to a value, the translator assigns a distribution of types to a value based on examples from the learning set.
% an idea closely related to existentially quantified types~\cite{Launchbury93lazyfunctional}.

@@

\begin{figure}
\begin{mathpar}
\hspace{-1cm} %no idea why, but this is better than \centering here
\inferrule* [Right=Empty]
{\\}
{k:[\ast = 0]}
\and
\inferrule* [Right=bool\_int]
{(k,v) \in C \\ v \in \{0,1\} \\ k:\ptype}
{k:\ptype\update[int\pluseq 1,bool\pluseq 1]}
\and
\inferrule* [Right=bool]
{(k,v) \in C \\ v \in \{ON,OFF\} \\ k:\ptype}
{k:\ptype\update[bool\pluseq 1]}
\\
\and
\inferrule* [Right=bool\_resolve]
{k:\ptype \\ \ptype \models bool \geq 2 \land \ast \leq 1}
{k :: bool}
\\
\and
\inferrule* [Right=eq\_rule]
{k1 :: \tau \\ k2 :: \tau \\ \tau \in \mathcal{T}}
{eq(k1,k2) :: Rule}
\end{mathpar}
\caption{Type judgments for boolean equality rules with probabilistic types}
\label{fig:ptypes}
\end{figure}

>>>>

{
\setlength{\belowcaptionskip}{-15pt}
\begin{figure}[!htb]
    \centering
    \begin{minipage}{.25\textwidth}
	\begin{lstlisting} [label={lst:1.cnf},language=C,caption={1.cnf}]
[server]
foo = ON
[client]
bar = 1
	\end{lstlisting}
    \end{minipage}%
    \hspace{1cm}
    \begin{minipage}{0.25\textwidth}
	\begin{lstlisting} [label={lst:2.cnf},language=C,caption={2.cnf}]
[server]
foo = ON
[client]
bar = ON
	\end{lstlisting}
    \end{minipage}
    \hspace{1cm}
    \begin{minipage}{0.25\textwidth}
	\begin{lstlisting} [label={lst:2.cnf},language=C,caption={3.cnf}]
[server]
foo = OFF
[client]
bar = OFF
	\end{lstlisting}
    \end{minipage}
    \caption{A learning set of configuration files}
    \label{fig:tset}
\end{figure}
}

\para{Probabilistic types}
%\label{sec:ptypes}
An additional challenge is that it is not always possible to fully determine the type of key based on a single example value. 
For this reason, we introduce \textit{probabilistic types}, as contrasted with \textit{basic types}.
In \app, the set of basic types contains strings, file paths, integers, sizes, and booleans. 
Taking the configuration \ref{lst:1.cnf} \ennan{configuration 1.4 is too
far away from this place}, we can assume {\tt foo} is a boolean type by the grammar of MySQL,
  but the keyword {\tt bar} could either be a integer type or a boolean type.
Consider that we would like to learn a rule that the boolean keywords should have the same values ($eq(\texttt{foo},\texttt{bar})$).
We then have two potential situations; in the first case where {\tt bar}$::int$, we do not learn the above rule, but in the second case where {\tt bar}$::bool$, the rule is valid.
To resolve this ambiguity, instead of immediately assigning one type to a value, the translator assigns a distribution of types to a value based on examples from the learning set.
% an idea closely related to existentially quantified types~\cite{Launchbury93lazyfunctional}.

@@

{
\setlength{\abovecaptionskip}{-.05pt}
\setlength{\belowcaptionskip}{-15pt}
\begin{figure}
\begin{mathpar}
\hspace{-1cm} %no idea why, but this is better than \centering here
\inferrule* [Right=Empty]
{\\}
{k:[\ast = 0]}
\and
\inferrule* [Right=bool\_int]
{(k,v) \in C \\ v \in \{0,1\} \\ k:\ptype}
{k:\ptype\update[int\pluseq 1,bool\pluseq 1]}
\and
\inferrule* [Right=bool]
{(k,v) \in C \\ v \in \{ON,OFF\} \\ k:\ptype}
{k:\ptype\update[bool\pluseq 1]}
\\
\and
\inferrule* [Right=bool\_resolve]
{k:\ptype \\ \ptype \models bool \geq 2 \land \ast \leq 1}
{k :: bool}
\\
\and
\inferrule* [Right=eq\_rule]
{k1 :: \tau \\ k2 :: \tau \\ \tau \in \mathcal{T}}
{eq(k1,k2) :: Rule}
\end{mathpar}
\caption{Type judgments for boolean equality rules with probabilistic types}
\label{fig:ptypes}
\end{figure}
}
